Proposed Solution

### 2016-11-13 Ennan-Proposal/related.tex
intro, with news

Verification support to configuration files 
has been considered a promising way  
to tackle misconfiguration problems~\cite{xu15systems}.
Nevertheless, a practical misconfiguration
verification approach still remains an open problem.

@@

Huang {\em et al.} proposed a specification for configuration validation%
~\cite{huang15confvalley}. We will 
discuss this work in the misconfiguration
detection part.

>>>>

We now position our work to already existing work. Most of the 
work falls into, what is traditionally considered, system's research.

@@

We previously discussed ConfValley by Huang {\em et al.} proposed a specification for configuration validation%
~\cite{huang15confvalley}.

### 2016-11-13 Ennan-Proposal/travis.tex
intro, with news

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell77}, which we use to test a configuration file for membership
in the set of all correct files.
Traditionally, version space learning builds a model that defines membership using a series of disjunctions from a set of predefined hypotheses. However, we need  to use conjunctions to convey that a configuration file is only correct if it satisfies all the learned relations, as

>>>>

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell77}, which we use to test a configuration file for membership
in the set of all correct files.
Traditionally, version space learning builds a model that defines membership using a series of disjunctions from a set of predefined hypotheses.

We extend the \app's functionality

However, we need  to use conjunctions to convey that a configuration file is only correct if it satisfies all the learned relations, and disjunctions are used to state that it one compile if 
it satisfies one (or more
